Robotic cloth manipulation for clothing assistance task using Dynamic Movement Primitives

### 2017-08-28 paper/paper.tex
[minor] add DOI in paper.pdf

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{to_be_inserted_after_paper_is_accepted}

% ISBN
\acmISBN{1-58113-000-0/00/0010}

%Conference
\acmConference[AIR 2017]{Advances in Robotics}{June 28-July 02, 2017}{New Delhi, India}
\acmYear{2017}
\copyrightyear{2017}

\acmPrice{15.00}

@@

\section{Experiments}
\label{sec:experiments}
Robotic cloth manipulation task contains a dual arm humanoid robot Baxter. Setup of our system is shown in figure \ref{fig:setup}. We choose soft mannequin instead of a human for this experiment. Both the arms of mannequin are open and given support by a metallic stand, to avoid falling down. Mannequin is positioned in such a way so that it resides within limits of workspace of Baxter robot. Both the arms of mannequin are facing towards robot. A Kinect V2 \cite{microsoft2014kinect} sensor is mounted on LCD display of Baxter robot. Kinect sensor can see the mannequin and clothing article and provides depth information, which is necessary for mannequin tracking. The clothing article is put in the arms of Baxter robot manually before starting experiment.

>>>>

\copyrightyear{2017}
\acmYear{2017}

% Copyright
\setcopyright{acmcopyright}

%Conference
\acmConference{AIR '17}{June 28-July 2, 2017}{New Delhi, India}
\acmPrice{15.00}

%ISBN
\acmISBN{978-1-4503-5294-9/17/06}

% DOI
\acmDOI{10.1145/3132446.3134878}

@@

\section{Experiments}
\label{sec:experiments}
Robotic cloth manipulation task contains a dual arm humanoid robot Baxter. Setup of our system is shown in figure \ref{fig:setup}. We choose soft mannequin instead of a human for this experiment. Both the arms of mannequin are open and given support by a metallic stand, to avoid falling down the arms. Mannequin is positioned in such a way so that it resides within limits of workspace of Baxter robot. Both the arms of mannequin are facing towards robot. A Kinect V2 \cite{microsoft2014kinect} sensor is mounted on LCD display of Baxter robot. Kinect sensor can see the mannequin and clothing article and provides depth information, which is necessary for mannequin tracking. The clothing article is put in the arms of Baxter robot manually before starting experiment.
